---
output: github_document
bibliography: bibliography.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ecdmdata

<!-- badges: start -->

[![R build status](https://github.com/tmsalab/ecdmdata/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/ecdmdata/actions)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
<!-- badges: end -->


The goal of `ecdmdata` is to provide a set of an example assessment data sets
for psychometric modeling.

## Installation

You can install `ecdmdata` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tmsalab/ecdmdata")
```

## Data Sets Included

- Examination for the Certificate of Proficiency in English (ECPE) [@Templin:2013:DCMECPE]. 
    - `items_ecpe`, N = 2922 subject responses to J = 28 items.
    - `qmatrix_ecpe`, J = 28 items and K = 3 traits. 
- Fraction Addition and Subtraction [@Tatsuoka:1984:FractionSubtraction].
    - `items_fractions`: N = 536 subject responses to J = 20 items.
    - `qmatrix_fractions`: J = 20 items and K = 8 traits. 
- Revised PSVT:R [@Culpepper:2017:ChoiceIRT].
    - `items_spatial`: N = 516 subject responses to J = 30 items.

## Authors

James Joseph Balamuta and Steven Andrew Culpepper

## Citing the `ecdmdata` package

To ensure future development of the package, please cite `ecdmdata`
package if used during an analysis or simulation study. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("ecdmdata")
```

## License

MIT

## References
