---
output: github_document
bibliography: bibliography.bib
csl: apa-single-spaced.csl
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# edmdata

<!-- badges: start -->
[![R build status](https://github.com/tmsalab/edmdata/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/edmdata/actions)
[![Package-License](http://img.shields.io/badge/license-MIT-brightgreen.svg?style=flat)](https://opensource.org/licenses/MIT)
[![CRAN status](https://www.r-pkg.org/badges/version/edmdata)](https://CRAN.R-project.org/package=edmdata)
<!-- badges: end -->

The goal of `edmdata` is to provide a set of an example assessment data sets
for psychometric modeling.

## Installation

You can install `edmdata` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tmsalab/edmdata")
```

```{r echo = FALSE}
library("edmdata")
```

## Data Sets Included

- Examination for the Certificate of Proficiency in English (ECPE) [@Templin:2013:DCMECPE; @Templin:2014:HierarchicalDCM]. 
    - `items_ecpe`: N = `r nrow(items_ecpe)` subject responses to J = `r ncol(items_ecpe)` items.
    - `qmatrix_ecpe`: J = `r nrow(qmatrix_ecpe)` items and K = `r ncol(qmatrix_ecpe)` traits. 
    - **TMSA Papers:** @Culpepper:2019:ErRUM
- Fraction Addition and Subtraction [@Tatsuoka:1984:FractionSubtraction; @Tatsuoka:2002:FractionSubtractionRelease].
    - `items_fractions`: N = `r nrow(items_fractions)` subject responses to J = `r ncol(items_fractions)` items.
    - `qmatrix_fractions`: J = `r nrow(items_fractions)` items and K = `r ncol(items_fractions)` traits. 
    - **TMSA Papers:** @Chen:2021:InferK, @Chen:2020:SLCMDC, @Culpepper:2019:EGDM, @Culpepper:2019:ErRUM, @Chen:2018:EDINA
- Elementary Probability Theory [@Heller:2013:ProbabilityKS].
    - `items_probability_part_one_full`: N = `r nrow(items_probability_part_one_full)`
      subject responses to J = `r ncol(items_probability_part_one_full)` items.
    - `items_probability_part_one_reduced`: N = `r nrow(items_probability_part_one_reduced)`
      subject responses to J = `r ncol(items_probability_part_one_reduced)` items.
    - `qmatrix_probability_part_one`: J = `r nrow(qmatrix_probability_part_one)` 
     items and K = `r ncol(qmatrix_probability_part_one)` traits. 
    - **TMSA Papers:** @Chen:2021:InferK
- Revised PSVT:R [@Yoon:2011:RevisedPSVTR; @Culpepper:2017:ChoiceIRT].
    - `items_revised_psvtr`: N = `r nrow(items_revised_psvtr)` subject responses
      to J = `r ncol(items_revised_psvtr)` items.
    - **TMSA Papers:** @Culpepper:2017:ChoiceIRT, @Culpepper:2015:BayesianDINA
- Subset of Early Childhood Longitudinal Study, Kindergarten Class of 1998-1999's
  Approaches to Learning [@ECLSK:2010:ATLData].
    - `items_ordered_eclsk_atl`: N = `r nrow(items_ordered_eclsk_atl)` subject responses
      to J = `r ncol(items_ordered_eclsk_atl)` items.
    - **TMSA Papers:** @Culpepper:2019:EODM
- Trends in International Mathematics and Science Study 2015 (TIMSS) Grade 8
  Student Background Survey Item Responses [@TIMSS:2015:Background].
    - `items_ordered_timss15_background`: N = `r nrow(items_ordered_timss15_background)` subject responses
      to J = `r ncol(items_ordered_timss15_background)` items.
- Programme for International Student Assessment (PISA) 2012
  U.S. Student Questionnaire Problem-Solving Vignettes [@Culpepper:2021:OHOEGDM].
    - `items_ordered_pisa12_us_vignette`: 
      N = `r nrow(items_ordered_pisa12_us_vignette)`
      subject responses to J = `r ncol(items_ordered_pisa12_us_vignette)` items.
- Programme for International Student Assessment (PISA) 2012
  U.S. Math Assessment.
    - `items_pisa12_us_math`: 
      N = `r nrow(items_pisa12_us_math)`
      subject responses to J = `r ncol(items_pisa12_us_math)` items.
- Last Series of the Standard Progressive Matrices (SPM-LS) [@Raven:1941:SPM; @Myszkowski:2018:IRTSPMLS; @Robitzsch:2020:IRTRCLMSPMLS].
    - `items_spm_ls`: N = `r nrow(items_spm_ls)`
      subject responses to J = `r ncol(items_spm_ls)` items.
- Human Connectome Project's Penn Progressive Matrices Fluid Intelligence Assessment
    - `items_hcp_penn_matrix`: N = `r nrow(items_hcp_penn_matrix)`
      subject responses to J = `r ncol(items_hcp_penn_matrix)` items.
    - `items_hcp_penn_matrix_missing`: N = `r nrow(items_hcp_penn_matrix_missing)`
      subject responses with missing data indicators to J = `r ncol(items_hcp_penn_matrix_missing)` items.
- Experimental Matrix Reasoning Test [@OpenPsychometrics:2012:IQ1].
    - `items_matrix_reasoning`: N = `r nrow(items_matrix_reasoning)`
      subject responses to J = `r ncol(items_matrix_reasoning)` items.
    - **TMSA Papers:** @Chen:2020:SLCMDC
- Taylor Manifest Anxiety Scale [@Taylor:1953:TMI; @OpenPsychometrics:2012:TaylorAnxietyScale].
    - `items_taylor_manifest_anxiety_scale`: N = `r nrow(items_taylor_manifest_anxiety_scale)`
      subject responses to J = `r ncol(items_taylor_manifest_anxiety_scale)` items.
- Narcissistic Personality Inventory [@Raskin:1988:NPI; @OpenPsychometrics:2013:NPI].
    - `items_narcissistic_personality_inventory`: N = `r nrow(items_narcissistic_personality_inventory)`
      subject responses to J = `r ncol(items_narcissistic_personality_inventory)` items.
- Pre-generated identified Q matrices.
    - `qmatrix_oracle_k2_j12`: 12 items and 2 traits.
    - `qmatrix_oracle_k3_j20`: 20 items and 3 traits.
    - `qmatrix_oracle_k4_j20`: 20 items and 4 traits.
    - `qmatrix_oracle_k5_j30`: 30 items and 5 traits.
- Pre-generated strategy sets. 
    - `strategy_oracle_k3_j20_s2`: 20 items, 3 traits, and 2 strategies.
    - `strategy_oracle_k3_j30_s2`: 30 items, 3 traits, and 2 strategies.
    - `strategy_oracle_k3_j40_s2`: 40 items, 3 traits, and 2 strategies.
    - `strategy_oracle_k3_j50_s2`: 50 items, 3 traits, and 2 strategies.
    - `strategy_oracle_k4_j20_s2`: 20 items, 4 traits, and 2 strategies.
    - `strategy_oracle_k4_j30_s2`: 30 items, 4 traits, and 2 strategies.
    - `strategy_oracle_k4_j40_s2`: 40 items, 4 traits, and 2 strategies.
    - `strategy_oracle_k4_j50_s2`: 50 items, 4 traits, and 2 strategies.


## Using data in the package

There are two ways to access the data contained within this package.

The first is to load the package itself and type the name of a data set.
This approach takes advantage of *R*’s lazy loading mechansim, which
avoids loading the data until it is used in *R* session. For details on
how lazy loading works, please see [Section 1.17: Lazy
Loading](https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Lazy-loading)
of the [R
Internals](https://cran.r-project.org/doc/manuals/r-release/R-ints.html)
manual.

``` r
# Load the `edmdata` package
library("edmdata")

# See the first 10 observations of the `items_revised_psvtr` dataset
head(items_revised_psvtr)

# View the help documentation for `items_revised_psvtr`
?items_revised_psvtr
```

The second approach is to use the `data()` command to load data on the
fly without loading the package. After using `data()`, the data set
will be available to use under the given name. 

``` r
# Loading `items_revised_psvtr` without a `library(edmdata)` call
data("items_revised_psvtr", package = "edmdata")

# See the first 10 observations of the `items_revised_psvtr` dataset
head(items_revised_psvtr)

# View the help documentation for `items_revised_psvtr`
?items_revised_psvtr
```

## Build Scripts

Want to see how each data set was imported? Check out the
[`data-raw`](https://github.com/tmsalab/edmdata/tree/master/data-raw)
folder!

## Authors

James Joseph Balamuta, Steven Andrew Culpepper, Jeffrey Douglas

## Citing the `edmdata` package

To ensure future development of the package, please cite `edmdata`
package if used during an analysis or simulation study. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("edmdata")
```

## License

MIT

## References
