---
output: github_document
bibliography: bibliography.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ecdmdata

<!-- badges: start -->
[![R build status](https://github.com/tmsalab/ecdmdata/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/ecdmdata/actions)
[![Package-License](http://img.shields.io/badge/license-MIT-brightgreen.svg?style=flat)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

The goal of `ecdmdata` is to provide a set of an example assessment data sets
for psychometric modeling.

## Installation

You can install `ecdmdata` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tmsalab/ecdmdata")
```

```{r echo = FALSE}
library("ecdmdata")
```

## Data Sets Included

- Examination for the Certificate of Proficiency in English (ECPE) [@Templin:2013:DCMECPE]. 
    - `items_ecpe`: N = `r nrow(items_ecpe)` subject responses to J = `r ncol(items_ecpe)` items.
    - `qmatrix_ecpe`: J = `r nrow(qmatrix_ecpe)` items and K = `r ncol(qmatrix_ecpe)` traits. 
- Fraction Addition and Subtraction [@Tatsuoka:1984:FractionSubtraction; @Tatsuoka:2002:FractionSubtractionRelease].
    - `items_fractions`: N = `r nrow(items_fractions)` subject responses to J = `r ncol(items_fractions)` items.
    - `qmatrix_fractions`: J = `r nrow(items_fractions)` items and K = `r ncol(items_fractions)` traits. 
- Revised PSVT:R [@Yoon:2011:RevisedPSVTR; @Culpepper:2017:ChoiceIRT].
    - `items_revised_psvtr`: N = `r nrow(items_revised_psvtr)` subject responses
      to J = `r ncol(items_revised_psvtr)` items.
- Taylor Manifest Anxiety Scale [@Taylor:1953:TMI; @OpenPsychometrics:2012:TaylorAnxietyScale].
    - `items_taylor_manifest_anxiety_scale`: N = `r nrow(items_taylor_manifest_anxiety_scale)`
      subject responses to J = `r ncol(items_taylor_manifest_anxiety_scale)` items.
- Narcissistic Personality Inventory [@Raskin:1988:NPI; @OpenPsychometrics:2013:NPI].
    - `items_narcissistic_personality_inventory`: N = `r nrow(items_narcissistic_personality_inventory)`
      subject responses to J = `r ncol(items_narcissistic_personality_inventory)` items.
    
## Using data in the package

There are two ways to access the data contained within this package.

The first is to load the package itself and type the name of a data set.
This approach takes advantage of *R*’s lazy loading mechansim, which
avoids loading the data until it is used in *R* session. For details on
how lazy loading works, please see [Section 1.17: Lazy
Loading](https://cran.r-project.org/doc/manuals/r-release/R-ints.html#Lazy-loading)
of the [R
Internals](https://cran.r-project.org/doc/manuals/r-release/R-ints.html)
manual.

``` r
# Load the `ecdmdata` package
library("ecdmdata")

# See the first 10 observations of the `items_revised_psvtr` dataset
head(items_revised_psvtr)

# View the help documentation for `items_revised_psvtr`
?items_revised_psvtr
```

The second approach is to use the `data()` command to load data on the
fly without and type the name of a data set.

``` r
# Loading `items_revised_psvtr` without a `library(ucidata)` call
data("items_revised_psvtr", package = "ucidata")

# See the first 10 observations of the `items_revised_psvtr` dataset
head(items_revised_psvtr)

# View the help documentation for `items_revised_psvtr`
?items_revised_psvtr
```

## Build Scripts

Want to see how each data set was imported? Check out the
[`data-raw`](https://github.com/tmsalab/ecdmdata/tree/master/data-raw)
folder!

## Authors

James Joseph Balamuta, Steven Andrew Culpepper, Jeffrey Douglas

## Citing the `ecdmdata` package

To ensure future development of the package, please cite `ecdmdata`
package if used during an analysis or simulation study. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("ecdmdata")
```

## License

MIT

## References
