---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ecdmdatadata

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Travis-CI Build Status](https://travis-ci.org/tmsalab/ecdmdata.svg?branch=master)](https://travis-ci.org/tmsalab/ecdmdata)
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/ecdmdata)](https://cran.r-project.org/package=ecdmdata)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/ecdmdata)](http://www.r-pkg.org/pkg/ecdmdata)

The goal of `ecdmdatadata` is to provide a set of an example assessment data sets
for psychometric modeling.

## Installation

You can install ecdmdatadata from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tmsalab/ecdmdatadata")
```

## Data Sets Included

- `items_ecpe` / `qmatrix_ecpe`: Examination for the Certificate of Proficiency in English (ECPE), Templin, J. and Hoffman, L. (2013). 
- `items_fractions` / `qmatrix_fractions`: Fraction Addition and Subtraction, Tatsuoka, K. K. (1984).
- `items_spatial`: Revised PSVT:R, Culpepper and Balamuta (2013).
